Review: Crop adaptation through post-domestication introgression from wild relatives

### 2016-05-24 TiG_prospectus.tex
edits to prospectus

\section*{Introgression methods and recent applications}
The recent availability of genome-wide resequencing and reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq) data combined with new analytical methods have facilitated comprehensive study of introgression across a number of species.
\begin{enumerate}
\item{High-density marker data can be used with haplotype-based and other methods to assign specific genomic regions to a taxon of origin}
\item{In several instances, introgression has been found to be conserved across individuals and populations suggesting an adaptive role:}
	\begin{enumerate}
	\item{Introgression from Neanderthals and other archaic hominins into humans at loci controlling skin pigmentation, defense against pathogens, and tolerance of high altitude (reviewed in \cite{Racimo2015}})
	\end{enumerate} 
\item{\textbf{Table 1:} List and brief description of recently developed methods and examples of empirical studies employing these methods}
\item{}
\end{enumerate}

\section*{Crop adaptation through introgression}

@@

\cite{Hufford2013} \cite{Baute2015}

>>>>

\section*{Introgression methods and recent applications}
The recent availability of genome-wide resequencing and reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq) data combined with new analytical methods have facilitated comprehensive study of introgression across a number of species.
\begin{enumerate}
\item{High-density marker data can be used with haplotype-based and other methods to assign specific genomic regions to a taxon of origin}
\item{In several instances, introgression is conserved across individuals and populations suggesting an adaptive role:}
	\begin{enumerate}
	\item{Introgression from Neanderthals and other archaic hominins into humans at loci controlling skin pigmentation, defense against pathogens, and tolerance of high altitude (reviewed in \cite{Racimo2015}})
	\item{Introgression across butterfly species at protective color-pattern loci conferring M\"{u}llerian mimicry \cite{Heliconius2012}}
	\item{Adaptive introgression across mosquito species at a locus controlling insecticide resistance \cite{Norris2015}}
	\end{enumerate} 
\item{\textbf{Table 1:} List and brief description of recently developed methods and examples of empirical studies employing these methods}
\item{}
\end{enumerate}

\section*{Crop adaptation through introgression}
\cite{Hufford2013} \cite{Baute2015} \cite{Bredeson2015}

@@
